Weather covariance matrices as U_hyp for GR50

### 2021-01-15 R/Analysis_v0.6_weather_covariance_Uhyp_greenup.Rmd
Writeup for mash figure 2 covariance matrices

get_pw_filtered(m_gulf_gr_hyp, pw_thresh = 0.1, BF_thresh = 2) %>% 
  mutate(Type = case_when(grepl("ED_", covar_grid) ~ "data-driven",
                          grepl("Stand", covar_grid) ~ "canonical",
                          grepl("simple_het", covar_grid) ~ "canonical",
                          grepl("null", covar_grid) ~ "canonical",
                          grepl("identity", covar_grid) ~ "canonical",
                          grepl("equal_effects", covar_grid) ~ "canonical",
                          grepl("_and_Midwest", covar_grid) ~ "hyp",
                          grepl("Midwest", covar_grid) ~ "hyp",
                          grepl("Gulf", covar_grid) ~ "hyp",
                          TRUE ~ "other"
                          ))

@@

```
Not many SNPs with U_hyp loading > 10% and SNP with log10BF > 2:
Both GR: 10 & 9 SNPs   cgdd_12c_18d_Gulf_and_Midwest x2 (0.9 and 0.10)
Both FL: 2 SNPs        dyln_change_sec_Midwest

@@

Midw GR: 0 SNPs
Midw FL: 11 SNPs       cgdd_12c_gr2fl_Gulf_and_Midwest

@@

# Annotations with rice/thaliana functional annotation papers for specific SNPs
```{r}
library(AnnotationDbi)
txdb <- loadDb("~/Github/pvdiv-genome/Pvirgatum_516_v5.1.gene.txdb.sqlite")
not_all_na <- function(x) any(!is.na(x))
not_any_na <- function(x) all(!is.na(x))
region_size <- 20000

gg_annos <- pw_gg %>% 
  filter((cgdd_12c_18d_Gulf_and_Midwest.10 > .1 | tave_18d_Gulf_and_Midwest.6 > 0.1) & log10BayesFactor > 2) %>%
  mutate(CHR = Chr,
         start = Pos - (region_size/2),
         end = Pos + (region_size/2)) %>%
  pvdiv_table_topsnps(., type = "table", txdb = txdb)

gg_annos %>%
  inner_join(os_annos, by = c("Gene ID")) %>%
  left_join(osgene_key, by = c("OsGene" = "Symbol")) %>%
  dplyr::select(where(not_all_na))

top_annos <- pw_gg %>%
  filter(log10BayesFactor > 2) %>%
  mutate(CHR = Chr,
         start = Pos - (region_size/2),
         end = Pos + (region_size/2)) %>%
  pvdiv_table_topsnps(., type = "table", txdb = txdb) %>%
  inner_join(os_annos, by = c("Gene ID")) %>%
  left_join(osgene_key, by = c("OsGene" = "Symbol")) %>%
  dplyr::select(where(not_all_na)) %>%
  group_by(Chr, POS, `Gene ID`) %>%
  dplyr::slice(1)
```

@@

```{r}
annos_gg
```

>>>>

get_pw_filtered(m_midw_fl_hyp, pw_thresh = 0.1, BF_thresh = 2) %>% 
  mutate(Type = case_when(grepl("ED_", covar_grid) ~ "data-driven",
                          grepl("Stand", covar_grid) ~ "canonical",
                          grepl("simple_het", covar_grid) ~ "canonical",
                          grepl("null", covar_grid) ~ "canonical",
                          grepl("identity", covar_grid) ~ "canonical",
                          grepl("equal_effects", covar_grid) ~ "canonical",
                          grepl("_and_Midwest", covar_grid) ~ "hyp",
                          grepl("Midwest", covar_grid) ~ "hyp",
                          grepl("Gulf", covar_grid) ~ "hyp",
                          TRUE ~ "other"
                          ))

@@

```
Not many SNPs with U_hyp loading > 10% and SNP with log10BF > 2:
Both GR: 10 & 9 SNPs   cgdd_12c_18d_Gulf_and_Midwest x2 (0.9 and 0.10)
Both FL: 2 SNPs        dyln_change_sec_Midwest.7

@@

Midw GR: 0 SNPs
Midw FL: 11 SNPs       cgdd_12c_gr2fl_Gulf_and_Midwest.8

@@

# Annotations with rice/thaliana functional annotation papers for specific SNPs

@@

```{r}
annos_gg %>%
  filter(cgdd_12c_18d_Gulf_and_Midwest.10 > 0.05 |
           tave_18d_Gulf_and_Midwest.6 > 0.05) %>%
  dplyr::select(where(not_all_na))

annos_gamg %>%
  filter(cgdd_12c_18d_Gulf_and_Midwest.10 > 0.05 |
           cgdd_12c_18d_Gulf_and_Midwest.9 > 0.05) %>%
  dplyr::select(where(not_all_na))

annos_gamf %>%
  # dplyr::select(starts_with("dyln_change_sec"))
  filter(dyln_change_sec_Midwest.7 > 0.05) %>%
  dplyr::select(where(not_all_na))
annos_mf %>%
  # dplyr::select(starts_with("cgdd_12c_gr2fl_Gulf_and"))
  filter(cgdd_12c_gr2fl_Gulf_and_Midwest.8 > 0.05) %>%
  dplyr::select(where(not_all_na))
```
Not many SNPs with U_hyp loading > 10% and SNP with log10BF > 2:
Both GR: 10 & 9 SNPs   cgdd_12c_18d_Gulf_and_Midwest x2 (0.9 and 0.10)
Both FL: 2 SNPs        dyln_change_sec_Midwest.7

Midw GR: 0 SNPs
Midw FL: 11 SNPs       cgdd_12c_gr2fl_Gulf_and_Midwest.8
